When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-02-28 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
explained MLM betas

Consequently, we had to adapt the multi level model to incorporate this non-linear trend.
To apply the contrast to the *n*-back levels, we had to turn the variables into a factor, with two consequences:
Centered variables cannot be turned into factors, so we entered the variables in their raw form, and factors cannot be used as random slopes, so the model is now defined as:
$$
SV \sim level\ + d' + median RT + (1|subject)
$$
This means that the intercept still varies between subjects, but there are no random slopes anymore.
To provide more than one observation per factor level, we used the two rounds per level per subject, rather than levels per subject.
The ICC of the null model indicated that there is a correlation of $r=$`r round(model0_h2b_ICC, digits = 3)` between the SVs of a subject, i.e. that `r paste0(formatC(model0_h2b_ICC * 100, format = "f", digits = 2), "%")` of variance in SVs can be explained by differences between participants.
We did not use an optimization algorithm to improve the fit of the random intercept model.
A total of `r nrow(excl_cases_h2b)` data points from `r length(unique(excl_cases_h2b$subject))` participants were excluded, because the residuals exceeded 3 SD above the mean.
The results of the final model are displayed in Table\ \@ref(tab:H2b-results).

```{r H2b-results, echo=FALSE, message=FALSE, warning=FALSE}
kable(h2b_result.table,
        caption = "Results of the multi level model on the influence of n-back level (as a declining logistic contrast) and task performance on subjective values.",
        booktabs = T,                          # no vertical lines
        escape = F,                            # correctly print special characters)
        align = c("l",rep("r",6))) %>%         # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped")) %>%
    footnote(general = "$SE$ = standard error, $df$ = degrees of freedom, $SD$ = standard deviation.",
             escape = F,                    # correctly print special characters
             threeparttable = T)            # line breaks in the footnote
```

The model had an effect size of $f^{2}=$`r round(h2b_level_f2, digits = 2)` for the *n*-back levels and $f^{2}=$`r round(h2b_dprime_f2, digits = 2)` for *d'*, which are considered large and small, respectively [@Cohen1992].
This means that the *n*-back level explained `r paste0(formatC(h2b_level_f2 * 100, format = "f", digits = 2), "%")` and *d'* explained `r paste0(formatC(h2b_dprime_f2 * 100, format = "f", digits = 2), "%")` of variance in SVs relative to the unexplained variance, respectively.
The effect size of the median RT was $f^{2}=$`r format(round(h2b_medianRT_f2, digits = 2), nsmall = 2)`.

@@

The rmANOVA with different pre-defined contrasts showed that all fit the SVs to a different degree, and that the SVs do not simply decline linearly across *n*-back levels.
The best fit was a declining logistic curve, reflecting that the majority of participants preferred 1-back and that SVs for 2-back were also high, before having more interindividual variance for 3- and 4-back.
The MLM with the logistic contrast showed that the *n*-back level explained the majority of variance in SVs, while the performance measure *d'* also explained some variance in SVs, albeit small.
In both cases, the SVs decreased when the value of the predictor increased.
The median RT was not a significant predictor in this model, which was somewhat surprising because RT but not *d'* yielded significant differences across levels in the manipulation checks.
However, participants might have deliberately or subconsciously used the feedback they received at the end of each round, i.e. twice per *n*-back level, as an anchor during the effort discounting.
This feedback was based on correct responses and not on RT, so if participants based their effort discounting choices at least partly on this feedback, they were either motivated to repeat a task in which they perform well and/or they were reluctant to accept a larger reward for a task in which they did not perform well.

>>>>

Consequently, we had to adapt the multi level model to incorporate this non-linear trend.
To apply the contrast to the *n*-back levels, we had to turn the variables into a factor, with two consequences:
Centered variables cannot be turned into factors, so we entered the variable level in its raw form, and factors cannot be used as random slopes, so the model is now defined as:
$$
SV \sim level\ + d' + median RT + (1|subject)
$$
This means that the intercept still varies between subjects, but there are no random slopes anymore.
To provide more than one observation per factor level, we used the two rounds per level per subject, rather than levels per subject.
The ICC of the null model indicated that there is a correlation of $r=$`r round(model0_h2b_ICC, digits = 3)` between the SVs of a subject, i.e. that `r paste0(formatC(model0_h2b_ICC * 100, format = "f", digits = 2), "%")` of variance in SVs can be explained by differences between participants.
We did not use an optimization algorithm to improve the fit of the random intercept model.
A total of `r nrow(excl_cases_h2b)` data points from `r length(unique(excl_cases_h2b$subject))` participants were excluded, because the residuals exceeded 3 SD above the mean.
The results of the final model are displayed in Table\ \@ref(tab:H2b-results).

```{r H2b-results, echo=FALSE, message=FALSE, warning=FALSE}
kable(h2b_result.table,
        caption = "Results of the multi level model on the influence of n-back level (as a declining logistic contrast) and task performance on subjective values.",
        booktabs = T,                          # no vertical lines
        escape = F,                            # correctly print special characters)
        align = c("l",rep("r",7))) %>%         # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped")) %>%
    footnote(general = "$SE$ = standard error, $df$ = degrees of freedom, $SD$ = standard deviation.",
             escape = F,                    # correctly print special characters
             threeparttable = T)            # line breaks in the footnote
```

The model had an effect size of $f^{2}=$`r round(h2b_level_f2, digits = 2)` for the *n*-back levels and $f^{2}=$`r round(h2b_dprime_f2, digits = 2)` for *d'*, which are considered large and small, respectively [@Cohen1992].
This means that the *n*-back level explained `r paste0(formatC(h2b_level_f2 * 100, format = "f", digits = 2), "%")` and *d'* explained `r paste0(formatC(h2b_dprime_f2 * 100, format = "f", digits = 2), "%")` of variance in SVs relative to the unexplained variance, respectively.
The effect size of the median RT was $f^{2}=$`r format(round(h2b_medianRT_f2, digits = 2), nsmall = 2)`.
The beta coefficients indicated that with every *n*-back level, the SV decreased by `r as.numeric(h2b_result.table[2,"Beta"])`, and for every 1-unit increase in *d'*, the SV increased by `r as.numeric(h2b_result.table[3,"Beta"])`.

@@

The rmANOVA with different pre-defined contrasts showed that all fit the SVs to a different degree, and that the SVs do not simply decline linearly across *n*-back levels.
The best fit was a declining logistic curve, reflecting that the majority of participants preferred 1-back and that SVs for 2-back were also high, before having more interindividual variance for 3- and 4-back.
The MLM with the logistic contrast showed that the *n*-back level explained the majority of variance in SVs, while the performance measure *d'* also explained some variance in SVs, albeit small.
In both cases, the SVs decreased when the value of the predictor increased.
The median RT was not a significant predictor in this model, which was somewhat surprising because RT but not *d'* yielded significant differences across levels in the manipulation checks.
However, participants might have deliberately or subconsciously used the feedback they received at the end of each round, i.e. twice per *n*-back level, as an anchor during the effort discounting.
This feedback was based on correct responses and not on RT, so if participants based their effort discounting choices at least partly on this feedback, they were either motivated to repeat a task in which they performed well and/or they were reluctant to accept a larger reward for a task in which they did not perform well.
Since more participants reported effort avoidance as their motivation in the effort discounting than those who reported seeking a challenge, we can assume that they were more motivated to repeat a task in which they performed well because their good performance coincided with low effort.
